### 2019-03-29 0_abstract.tex
Apply Alex's comments to sections 1-4.

\begin{abstract}
% 129 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelopes of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench seeks to provide the ease of implementation and portability of
microbenchmarks, which makes comparisons between many systems
possible, with the ability to easily model a wide range of application
scenarios, giving it coverage approximating large benchmarks.

We conduct a comprehensive study with implementations of Task Bench in
13 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We use a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each system
and the impact of scenarious with varying dependence patterns. We also
study each system's scalability, and ability to hide communication and
mitigate load imbalance.
\end{abstract}

>>>>

\begin{abstract}
% 126 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelopes of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench seeks to provide the ease of implementation and portability of
microbenchmarks, which makes comparisons between many systems
possible, with the ability to model a wide range of application
scenarios, giving it coverage approximating large benchmarks.

We conduct a comprehensive study with implementations of Task Bench in
13 programming systems on up to 256 Haswell nodes of the Cori
supercomputer. We use a novel metric, \emph{minimum effective task
  granularity} to study the baseline runtime overhead of each system
and the impact of different dependence patterns. We also
study each system's scalability, and ability to hide communication and
mitigate load imbalance.
\end{abstract}

### 2019-03-29 1_introduction.tex
Apply Alex's comments to sections 1-4.

The challenge of parallel and distributed computation has lead to a
wide variety of proposals for programming models, languages, and
runtime systems. Some, like MPI~\cite{MPI}, have achieved widespread
usage while many more are in the research and development stage. Our
goal in this paper is to develop a meaningful and useful framework for
comparing the performance of parallel and distributed programming
systems.

@@

One approach to comparing the performance of different systems has
focused on the development of \emph{proxy-} or
\emph{mini-apps}. Because they embody the logic of a larger
application, but in reduced form, mini-apps can provide insight
without incurring the costly expense of developing a full-blown
application code. However, despite the name, our experience is that
mini-apps still requite significant investment to develop, especially
to a level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop the
mini-app in the first place. As a result, implementations of mini-apps
often do not reach a level of maturity required to compare
systems. Indeed, there are few such published studies, and none to our
knowledge that involve more than a handful of systems.

There is another important issue: How does one predict how
the performance of a mini-app generalizes to a full
application, even one closely related? Part of the problem here is
that weak and strong scaling, which are by far the most commonly
reported metrics for performance of both mini- and full applications,
do not directly characterize the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead with sufficiently large problem sizes. And strong
scaling does not separate the overhead of the underlying runtime
system from the growth in communication latencies, and potential
saturation of resources such as communication and I/O bandwidth, when
using progressively larger portions of the machine.

To address the first of these issues, we present Task Bench, a
\emph{parameterized} benchmark designed for exploring the performance
behaviors of parallel and distributed programming systems under a
variety of conditions. A critical property of Task Bench is that,
while able to express a wide variety of typical parallel programming
patterns, it is simple enough to be implemented with reasonable effort
to a level of quality sufficient for comparative studies.

@@

To isolate the contribution of the programming model's runtime system
to application performance, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively,
METG(50\%) is the smallest application task granularity which can be
executed while maintaining at least 50\% computational efficiency,
meaning that the application achieves at least 50\% of peak
performance. METG captures the essence of what is important in a weak
or strong scaling study, the behavior at the limit of scalability. For
weak scaling, METG(50\%) corresponds directly to the smallest problem
size that can be weak scaled with 50\% efficiency. For strong scaling,
METG(50\%) can be used to compute the scale at which performance can
be expected to dip below 50\% efficiency. A good rule of thumb is that
as long as an application's \emph{average} task granularity exceeds
METG(50\%), the application should achieve at least 50\% efficiently.

Task Bench and METG mitigate issues common in limit studies of runtime
systems for parallel and distributed programming. Such studies often
employ the metric \emph{tasks per second} (TPS), which is almost
universally measured with trivial (i.e., no) dependencies. While
phrased in terms of tasks, TPS can be measured for any system as long
as the application in question has identifiable units of work that run
to completion without interruption. TPS is an upper bound on
runtime-limited application throughput, but not a tight bound, as the
cost of non-trivial dependencies can be significant and may impact
scalability. This issue is easily fixed by running non-trivial
configurations of Task Bench.

@@

The following four sections each describe a contribution of this
paper:

>>>>

The challenge of parallel and distributed computation has lead to a
wide variety of proposals for programming models, languages, and
runtime systems. But while the features of these systems are widely
written about in the literature, comprehensive performance evaluations
of these systems remain difficult to find. Our
goal in this paper is to develop a meaningful and useful framework for
comparing the performance of parallel and distributed programming
systems.

@@

One approach to comparing the performance of different systems has
focused on the development of \emph{proxy-} or
\emph{mini-apps}. Because they distill the structure of a larger
application, mini-apps can provide insight
without the expense of developing a full-blown
application. However, despite the name, our experience is that
mini-apps still requite significant investment to develop, especially
to the level of quality needed for useful benchmarking. In many cases,
the effort to tune for performance exceeds the effort to develop the
mini-app in the first place. As a result, implementations of mini-apps
often do not reach the level of maturity required to compare
systems. Indeed, there are few such published studies, and none to our
knowledge that involve more than a handful of systems.

There is another important issue: How does one predict how
the performance of a mini-app generalizes to a full
application, even one closely related? Part of the problem here is
that weak and strong scaling, which are by far the most commonly
reported metrics for performance of both mini- and full applications,
do not directly characterize the performance of the underlying
programming system. Weak scaling can hide arbitrary amounts of runtime
system overhead with sufficiently large problem sizes, and strong
scaling does not separate runtime system overhead from other costs
(such as increased communication, among other things) when
using progressively larger portions of a machine.

To address the first issue, we present Task Bench, a
\emph{parameterized} benchmark designed for exploring the performance
behaviors of parallel and distributed programming systems under a
variety of conditions. A critical property of Task Bench is that,
while able to express a wide variety of typical parallel programming
patterns, it is simple enough to be implemented with reasonable effort
to a level of quality sufficient for comparative studies.

@@

To address the second issue and isolate the contribution of the programming model's runtime system
to application performance, we introduce a new metric called
\emph{minimum effective task granularity} (METG). Intuitively,
METG(50\%) is the smallest application task granularity which can be
executed while maintaining at least 50\% computational efficiency,
meaning that the application achieves at least 50\% of peak
performance on a given machine. METG captures the essence of what is important in a weak
or strong scaling study, the behavior at the limit of scalability. For
weak scaling, METG(50\%) corresponds directly to the smallest problem
size that can be weak scaled with 50\% efficiency. For strong scaling,
METG(50\%) can be used to compute the scale at which performance can
be expected to dip below 50\% efficiency.

A lower METG does not necessarily mean that performance will be
better. For example, two systems with METG(50\%) of 100~us and 1~ms,
respectively, running an application with an average task granularity
of 10~ms, are both likely to perform well. Only when the task
granularity approaches (or drops below) METG(50\%) is performance
likely to diverge. Thus METG helps to identify the regime in which a
given system is likely to perform well.

Task Bench and METG address issues common in limit studies of runtime
systems for parallel and distributed programming. Such studies often
employ the metric \emph{tasks per second} (TPS), which is almost
universally measured with trivial (i.e., no) dependencies. While
phrased in terms of tasks, TPS can be measured for any system as long
as the application in question has identifiable units of work that run
to completion without interruption. TPS is an upper bound on
runtime-limited application throughput, but not a tight bound, as the
cost of non-trivial dependencies can be significant and may impact
scalability. This issue is easily fixed by running non-trivial
configurations of Task Bench.

@@

The paper is organized as follows:

### 2019-03-29 2_metg.tex
Apply Alex's comments to sections 1-4.

The \emph{minimum effective task granularity}, METG(50\%), for an application $A$ is
the smallest average task granularity such that $A$
achieves overall efficiency exceeding 50\%. For example, in
a compute-bound application efficiency might be measured as the
percentage of the available FLOPS achieved. On a machine with a peak
capability of 1.26 TFLOPS per node, METG(50\%) would correspond to
smallest task granularity achieved while maintaining at least 0.63
TFLOPS. Absolute efficiency (i.e., FLOPS or B/s) as well
as parallel efficiency (relative to a sufficiently large problem size)
can be used.

Figure~\ref{fig:flops-mpi} shows the way in which METG is
calculated. The application, in this case an MPI implementation of the
Task Bench stencil pattern in Figure~\ref{fig:task-graphs-stencil}, is
run on a single Haswell node of Cori with a large enough problem size to
ensure that it achieves peak utilization of the machine. This confirms
that the application is properly configured and that the choice of
efficiency metric is achievable. Once this is established, the problem
size is repeatedly reduced while maintaining exactly the same hardware
configuration (in particular, the same number of nodes). The
expectation is that as problem size shrinks, the
efficiency will begin to drop and eventually approach zero. Systems
with lower runtime overheads maintain higher efficiency at smaller
problem sizes compared to systems with higher overheads.

To calculate METG, this data is replotted along axes of efficiency
(i.e., as a percentage of the peak FLOPS achieved) and task
granularity (i.e., $\text{wall time} \times \text{number of
  cores}/\text{number of tasks}$). Note that a \emph{task} is defined
broadly to be any continuously-executing unit of application code,
and thus it makes sense to discuss tasks even in systems
without an explicit notion of tasking, such as in MPI programs that
are written in a bulk synchronous style. In this case, the tasks run a
compute-bound kernel included in the Task Bench implementation,
described in more detail in Section~\ref{sec:task-bench}.

Figure~\ref{fig:efficiency-mpi} replots the data in
Figure~\ref{fig:flops-mpi}. In Figure~\ref{fig:efficiency-mpi}, we see that
efficiency starts near 100\%, and that initially task granularity
drops quickly with minimal change in efficiency. However as task
granularity shrinks, efficiency begins to drop as well, leading
eventually to a plateau in task granularity. Intuitively, this plateau
represents the fundamental baseline overhead of the system, the point
below which the system simply cannot execute tasks efficiently.

@@

METG is an appealing metric in part because it has a well-defined
relationship with quantities of interest to application developers,
namely weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the behavior of the MPI Task Bench stencil's weak and strong
scaling, respectively, at a variety of problem sizes. Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to show up at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed and begin to trend upward. At the
very bottom, the lines compress together as the fundamental
overhead of the MPI implementation dwarfs any gains from running smaller
problems. The shape of the curve at the bottom is the same
for both weak and strong scaling; this is precisely the shape of
the METG curve.

@@

The METG metric has one particularly useful property in comparison to
weak and strong scaling. Because METG is measured ``in place'' (i.e.,
without changing the number of nodes or cores available to the
application), it is possible to use METG to isolate effects that are
due to shrinking problem size from effects that are due to
increased communication latencies and other resource issues as
progressively larger portions of the machine are used.

>>>>

The \emph{minimum effective task granularity}, METG(50\%), for an application $A$ is
the smallest average task granularity (i.e., task duration) such that $A$
achieves overall efficiency exceeding 50\%. For example, in
a compute-bound application efficiency might be measured as the
percentage of the available FLOPS achieved. On a machine with a peak
capability of 1.26 TFLOPS per node, METG(50\%) would correspond to
the smallest task granularity achieved while maintaining at least 0.63
TFLOPS. Relative parallel efficiency (vs a sufficiently large problem
size) can also be used in cases where the application isn't easily
characterized by peak resource usage.

Figures~\ref{fig:flops-mpi} and \ref{fig:efficiency-mpi} show how METG is
calculated. The application, in this case an MPI implementation of the
Task Bench stencil pattern in Figure~\ref{fig:task-graphs-stencil}, is
run on a single Haswell node of Cori with a problem size large enough to
ensure that it achieves peak FLOPS. This starting point confirms
that the application is properly configured and that the choice of
efficiency metric is achievable. The problem
size is then repeatedly reduced while maintaining exactly the same hardware
configuration (in particular, the same number of nodes). The
expectation is that as problem size shrinks,
performance will begin to drop and eventually approach zero, as shown in Figure~\ref{fig:flops-mpi}. Systems
with lower runtime overheads maintain higher performance at smaller
problem sizes compared to systems with higher overheads.

To calculate METG, the data is replotted along axes of efficiency
(i.e., as a percentage of the peak FLOPS achieved) and task
granularity (i.e., $\text{wall time} \times \text{number of
  cores}/\text{number of tasks}$), as shown in Figure~\ref{fig:efficiency-mpi}. Note that a \emph{task} is defined
broadly to be any continuously-executing unit of application code,
and thus it makes sense to discuss tasks even in systems
without an explicit notion of tasking, such as in MPI programs that
are written in a bulk synchronous style. In this case, the tasks run a
compute-bound kernel included in the Task Bench implementation,
described in more detail in Section~\ref{sec:task-bench}.

In Figure~\ref{fig:efficiency-mpi}, we see that
efficiency starts near 100\%, and that initially task granularity
drops quickly with minimal change in efficiency. However as task
granularity shrinks further, efficiency begins to drop as well, leading
eventually to a plateau in task granularity. Intuitively, this plateau
represents the fundamental baseline overhead of the system, the point
below which the system simply cannot execute tasks efficiently.

@@

METG is an appealing metric in part because it has a well-defined
relationship with quantities of interest to application developers,
namely weak and strong scaling. Figures~\ref{fig:weak-scaling-mpi} and
\ref{fig:strong-scaling-mpi} show the behavior of the MPI Task Bench stencil's weak and strong
scaling, respectively, at a variety of problem sizes. Intuitively, at
larger problem sizes MPI is perfectly efficient. This can be seen at
the top of each figure, with flat lines when weak scaling and
ideally-sloped downward lines when strong scaling. Inefficiency begins
to show at smaller problem sizes, towards the bottom of the graph,
where lines become more compressed. At the
very bottom, the lines compress together as running time becomes dominated by overhead. The shape of the curve at the bottom is the same
for both weak and strong scaling; this is the shape of
the METG curve.

@@

The METG metric has another useful property. Because METG is measured ``in place'' (i.e.,
without changing the number of nodes or cores available to the
application), METG isolates effects that are
due to shrinking problem size from effects that are due to
increased communication and other resource issues as
progressively larger portions of the machine are used.

### 2019-03-29 3_task_bench.tex
Tweak spacing around figure captions.
Apply Alex's comments to sections 1-4.

\input{f5_task_graphs}

To measure properties such as METG for a wide variety of
systems and application scenarios, we developed a novel
\emph{parameterized} benchmark called Task Bench. Task Bench
implementations execute a \emph{task graph}, with tasks for each point
in an \emph{iteration space} and dependencies between tasks determined
by a \emph{dependence relation}. A task that depends on another task
must execute after that task, and receives the output data from that
task as input. Each task can execute any one of a
number of kernels (compute-bound, memory-bound, etc.) and can generate
a configurable amount of output to control the amount of communication
performed with each task dependency. Thus Task Bench can be used to
rapidly explore a large space of possible application scenarios to
understand the performance of parallel and
distributed languages and runtime systems.

For simplicity but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Many problems can be described by a task graph of
constant width, in which case the iteration space is rectangular, but
Task Bench is capable of handling non-rectangular iteration spaces,
such as required by sweeps and tree-based dependence
patterns. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, each column $i$ corresponds to all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column of the task graph will be
assigned to execute on a different processor core.

Dependencies between tasks are controlled by a configurable dependence
relation. Dependencies point backwards in time. The
dependence relation enumerates, for each task, the set of tasks in the
previous time step that task depends on. This permits a wide variety
of dependence patterns to be implemented that are relevant to real
applications in high-performance scientific computing and data analysis: stencils,
sweeps, FFTs, trees, and so on. Dependence patterns may also be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. Table~\ref{tab:equations} show equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.

\input{t0_equations}

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The core aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all cases, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the Task Bench core library manages the
parsing of input parameters and the display out output results,
ensuring that all implementations behave in a uniform manner, and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 13 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being typical.

The Task Bench core library is fully
validating. Because the task graph configuration is explicitly
represented (though unmaterialized) in Task Bench, this representation
can be queried to determine exactly what dependencies a task should
expect. The output of every task in Task Bench is unique,
and all inputs are verified. An assertion is thrown if validation
fails. This level of self-checking ensures that every execution of Task Bench, if it
completes successfully, is correct. This validation provides high
assurance that all Task Bench implementations are correct, and
safeguards against corner cases that may only be exercised at
scale. An evaluation of the performance impact of
this validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

Task Bench provides two main kernels which can be called from tasks,
which are compute- and memory-bound, respectively. The compute-bound
kernel executes a tight loop and is hand-written using AVX2 FMA
intrinsics. The memory-bound kernel performs sequential reads and
writes over an array, and is again hand-optimized with AVX2
intrinsics. The duration of both kernels can be configured by setting
the number of iterations to execute; we use this ability to simulate
the effects of varying application problem sizes. The memory-bound
kernel is carefully written to keep the working set size constant as
the number of iterations decrease, to avoid unwanted speedups due to
cache effects.

>>>>

To measure a wide variety of
systems and application scenarios, we developed a novel
\emph{parameterized} benchmark called Task Bench. Task Bench
implementations execute a \emph{task graph}, with tasks for each point
in an \emph{iteration space} and dependencies between tasks determined
by a \emph{dependence relation}. A task that depends on another task
must execute after that task, and receives the output data from that
task as input. Each task can execute any one of a
number of kernels (compute-bound, memory-bound, etc.) and can generate
a configurable amount of output to control the amount of communication
performed with each task dependency. Thus Task Bench can explore a large space of application scenarios to
understand the performance of parallel and
distributed programming systems.

For simplicity, but without loss of generality, the iteration space in
Task Bench is constrained to be 2-dimensional, with time along
the vertical axis and parallel tasks along the
horizontal. Tasks can depend only on tasks from the immediately
preceding time step. Figure~\ref{fig:task-graphs} shows a number of sample task
graphs that can be implemented with Task Bench. Note that layout is
significant---in particular, each column $i$ corresponds to all tasks
with index $i$ in the iteration space over all the time
steps. Generally speaking each column of the task graph will be
assigned to execute on a different processor core.

Dependencies between tasks are controlled by a configurable dependence
relation. The
dependence relation enumerates, for each task, the set of tasks in the
previous time step that task depends on. This permits a wide variety
of dependence patterns to be implemented that are relevant to real
applications in high-performance scientific computing and data analysis: stencils,
sweeps, FFTs, trees, and so on. Dependence patterns may also be
parameterized, such as picking the $K$ nearest neighbors, or $K$
distant neighbors. Table~\ref{tab:equations} show equations for the
dependence relations of the patterns in Figure~\ref{fig:task-graphs},
where $t$ is timestep, $i$ is column, and $W$ is the width of the task
graph.

\input{f5_task_graphs}
\input{t0_equations}

Despite its generality, Task Bench is easy to implement, making it
tractable to develop a suite of high-quality implementations. The core aspects of Task Bench, such as generating
task graphs and enumerating dependencies, are encapsulated in a core
library that is shared among all the Task Bench implementations. The
core library also includes implementations of the kernels, ensuring
that the kernels are identical in all cases, eliminating a potential
source of performance disparity that can be a pitfall for
implementations of mini-apps. Finally, the Task Bench core library manages the
parsing of input parameters and the display of output results,
ensuring that all implementations behave in a uniform manner, and can
be scripted consistently. Because much of the functionality needed for
a Task Bench implementation is in the core library, implementations of
Task Bench are small: Our 13 Task Bench implementations range from 88
to 1500 lines, with several hundred lines being typical.

The Task Bench core library is fully
validating. Because the task graph configuration is explicitly
represented (though unmaterialized) in Task Bench, this representation
can be queried to determine exactly what dependencies a task should
expect. The output of every task in Task Bench is unique,
and all inputs are verified. An assertion is thrown if validation
fails. This level of self-checking ensures that every execution of Task Bench, if it
completes successfully, is correct. An evaluation of the impact of
validation showed it to be less than 3\% at the smallest task
granularities in any Task Bench implementation, with a negligible
effect on overall results.

Task Bench provides two main kernels that can be called from tasks,
which are compute- and memory-bound, respectively. The compute-bound
kernel executes a tight loop and is hand-written using AVX2 FMA
intrinsics. The memory-bound kernel performs sequential reads and
writes over an array, and is again hand-optimized with AVX2
intrinsics. The duration of both kernels can be configured by setting
the number of iterations to execute; we use this ability to simulate
the effects of varying application problem sizes. The memory-bound
kernel is carefully written to keep the working set size constant as
the number of iterations decrease, to avoid unwanted speedups due to
cache effects.

### 2019-03-29 4_implementation.tex
Apply Alex's comments to section 5.
Apply Alex's comments to sections 1-4.

Chapel~\cite{Chapel07} is an explicitly parallel programming language
that follows a \emph{multi-resolution} approach to parallel
programming, with support for parallelism at a variety of
levels. Chapel's core features are a partitioned global address space
(PGAS), a data model for the distribution of data structures, tasks, and
synchronization primitives. Certain operations can be lifted to entire arrays, enabling forms of data-parallelism. Chapel thus permits a great deal of
flexibility in the choice of implementation strategy for applications.

For Task Bench, we decided to target a low-level implementation in
Chapel, using explicit task instantiation (via
\lstinline[language=Chapel]{coforall}), bulk access to distributed
arrays for efficient data movement, and atomic integers for
synchronization. This approach is a good match for Task Bench, as the
Task Bench core provides implementations of the kernels.

@@

Charm++~\cite{Charmpp93} is an explicitly parallel programming system
based on the actor model. Actors, or
\emph{chares}, are objects that live in their own address space and
can be migrated automatically between nodes to
balance load. Chares send messages to other chares via a
form of remote procedure call (RPC). Calling a method of another chare
is the primary form of synchronization and data movement in
Charm++. Additional support is provided for collective operations
between chares.

Our Task Bench implementation is straightforward: we create a chare
array for the task graph, with one chare for each column of the task graph. Methods are
used to implement dependencies, and a task is executed as soon as its
dependencies are all available. Collectives are used to synchronize the
completion of the task graph execution.

@@

MPI~\cite{MPI} is the standard message-passing API for
programming supercomputers and remains the most widely used programming
model in high-performance scientific computing today. Our
MPI implementation of Task Bench represents the common case of bulk synchronous programs with distinct computation and
communication phases. We use \lstinline[language=C++]{MPI_Isend} and
\lstinline[language=C++]{MPI_Irecv} to implement the communication
phase, posting receives before sends. Each task dependency maps to one
send/receive pair in MPI. Despite the relatively straightforward
design, our MPI implementation is among the best performing.

For completeness, we also explored the use of additional MPI calls:
namely buffered sends (\lstinline[language=C++]{MPI_Bsend}),
broadcasts (\lstinline[language=C++]{MPI_Bcast}), and all-to-all
communication (\lstinline[language=C++]{MPI_Alltoallv}). For the
configurations used in our evaluation, we found non-blocking sends and
receives to be the best performing, often by a wide margin.

@@

PaRSEC is a task-based programming system supporting two distinct
programming models: \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}.  PTG is a dataflow model in which programmers
write a concise, algebraic description of the tasks and dataflows in
the program. This compressed representation is expanded into a full
task graph by a source-to-source compiler. PTG is therefore a more
limited programming model, but can potentially provide better
performance because the graph description is amenable to static
analysis and can be pruned efficiently for better horizontal
scalability.

In the DTD model, tasks are enumerated in program order (by
dynamically executing the program), and dependencies between tasks are
identified automatically based on the input and output data of tasks. 
A task depends on another task if it reads data written by the other task,
and the data is copied automatically if the two tasks are executed on
different nodes. While the basic DTD model is implicitly parallel
because the system is responsible for the discovery of parallelism, to
achieve horizontal scalability, the program is executed in a
SPMD fashion on all nodes, and the user is responsible for eliding
tasks that are not directly connected to those that are to be executed
on the current node.

@@

In Regent tasks are executed sequentially and parallelism is
discovered automatically based on the data that is read or written by
tasks. Regent programs are agnostic to the machine architecture and
are separately \emph{mapped} for execution on a distributed memory
system. Copies are inserted automatically by the compiler and runtime
whenever data is read on a different node from where it is written.

The Regent compiler performs control replication to slice the Regent
program into \emph{shards} of execution which can scalably execute on
large numbers of nodes.

@@

Spark's programming model is based on \emph{functional parallelism}, a
generalization of the MapReduce programming
model~\cite{MapReduce04}. The core computational abstraction in Spark
are operators such as map, reduce, filter, join, etc. which by virtue
of being pure functions are trivially known to be
parallelizable. Functions in Spark operate on \emph{resilient
  distributed datasets} (RDDs), which are globally-visible,
dynamically single-assignment data structures that are cached in memory
and written to disk for durability. One of Spark's primary
optimizations therefore is the caching of RDDs to avoid unnecessary
disk traffic, resulting in substantial speedups over MapReduce.

@@

TensorFlow~\cite{TensorFlow15} is a programming system intended for
the executing deep learning workloads, widely used in industrial data
center applications. Although TensorFlow's high-level API exposes
concepts specific to machine learning, internally TensorFlow is
implemented as a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs are written by creating nodes in the
task graph, and then connecting these nodes with edges to implement
the desired dataflow. Task graphs are composed in a high-level
language such as Python, but then serialized and run by an efficient
execution engine written in C++.

>>>>

Chapel~\cite{Chapel07} is an explicitly parallel programming language
that follows a \emph{multi-resolution} approach to parallel
programming, with support for parallelism at a variety of
levels. Chapel's core features are a partitioned global address space
(PGAS), data distributions, tasks, and
synchronization primitives, and array promotion. For Task Bench, we decided to target a low-level implementation in
Chapel, using explicit task instantiation (via
\lstinline[language=Chapel]{coforall}), bulk access to distributed
arrays for efficient data movement, and atomic integers for
synchronization.

@@

Charm++~\cite{Charmpp93} is an explicitly parallel programming system
based on the actor model. Actors, or
\emph{chares}, are objects that live in their own address space;
chares communicate data and synchronize via messages, and can be moved
to balance load. Our Task Bench implementation uses a chare
array for the task graph, with one chare for each column of the task graph. Messages are
used to implement dependencies, and a task is executed as soon as its
dependencies are all available. Collectives are used to synchronize the
completion of the task graph execution.

@@

Our MPI~\cite{MPI} implementation of Task Bench represents the common
case of bulk synchronous programs with distinct computation and
communication phases. We experimented with a variety of implementation
strategies and found the best performing to be using
\lstinline[language=C++]{MPI_Isend} and
\lstinline[language=C++]{MPI_Irecv} to implement the communication
phase, posting receives before sends. Each task dependency maps to one
send/receive pair in MPI.

@@

PaRSEC is a task-based programming system supporting two distinct
programming models: \emph{parameterized task graphs}
(PTG)~\cite{PARSEC13} and \emph{dynamic task discovery}
(DTD)~\cite{PARSEC_DTD}.  PTG is a dataflow model in which programmers
write a concise, algebraic description of the tasks and dataflows in
the program. This compressed representation is expanded into a full
task graph by a source-to-source compiler.

In the DTD model, tasks are enumerated in program order (by
executing the program), and dependencies between tasks are
identified automatically based on the input and output data of tasks. 
A task depends on another task if it reads data written by the other task,
and the data is copied automatically if the two tasks are executed on
different nodes. While the basic DTD model is implicitly parallel
because the system is responsible for the discovery of parallelism, to
achieve horizontal scalability, the program is executed in a
SPMD fashion on all nodes, and the user is responsible for eliding
tasks that are not directly connected to those that are to be executed
on the current node.

@@

@@

The core abstractions in Spark are functional operators such as map,
reduce, filter, join, etc. Functions in Spark operate on
\emph{resilient
  distributed datasets} (RDDs), which are globally-visible,
dynamically single-assignment data structures that are cached in memory
and written to disk for durability. One of Spark's primary
optimizations therefore is the caching of RDDs to avoid unnecessary
disk traffic.

@@

TensorFlow~\cite{TensorFlow15} is a programming system intended for
the executing deep learning workloads, widely used in industrial data
center applications. Although TensorFlow's high-level API exposes
concepts specific to machine learning, internally TensorFlow is
implemented as a task graph execution engine, making it a good fit for
Task Bench. TensorFlow programs are written by creating nodes in the
task graph, and then connecting these nodes with edges to implement
the desired dataflow. Task graphs are composed in a high-level
language such as Python, but then serialized and run by an
execution engine written in C++.
